\documentclass[a4paper,11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\usepackage{times}
\usepackage[hidelinks]{hyperref}

\begin{document}
\thispagestyle{empty}


\textbf{Senior Software Engineer (Python)}\\[0.5em]

Dear Hiring Manager,\\[0.2em]

I am writing to express my interest in the Senior Software Engineer (Python) position. With over eight years of hands-on experience building scalable backend systems, cloud-native architectures, and high-performance distributed applications, I have consistently delivered solutions that combine engineering excellence with real business impact.

In my recent role, I led the development of multiple microservices, AI-driven internal tools, and ML-powered automation initiatives. Notably, I architected an ML-based rebill optimization system that improved transaction success rates by 15\%, and built a RAG-based chatbot that reduced manual data lookup time by 80\% for over 100 internal users. I also implemented a high-throughput NATS messaging architecture that reduced system latency by 50\% and increased reliability by 40\%.

Before that, I designed and delivered the core architecture for a loyalty platform supporting 5,000+ active users, integrated Stripe’s subscription management achieving a 99.99\% payment success rate, and reduced deployment time by 60\% through CI/CD automation. Across all roles, I have been deeply involved in Python development, serverless computing, event-driven systems, and performance optimization, always with a focus on measurable outcomes.

At sellanycar.com, I worked with scikit-learn, PyTorch, and OpenCV to build an image-processing system.

I bring expertise in Python, and its frameworks (FastAPI, Django, Django REST Framework), AWS, CI/CD pipelines, microservices, DevOps automations. More importantly, I bring a problem-solving mindset, strong ownership, and a commitment to building systems that are reliable, scalable, and maintainable.

I am excited about the opportunity to contribute my technical depth, architectural thinking, and product-oriented approach to your engineering team. I would welcome the chance to discuss how my experience can support your team’s goals and help drive the next stage of your platform’s evolution.

Thank you for your time and consideration.

Sincerely,

Mehdi Raza\\
\texttt{\href{https://linkedin.com/in/mehdi-raza-jaffri}{https://linkedin.com/in/mehdi-raza-jaffri}}\\
\texttt{\href{https://mehdiraza.dev}{https://mehdiraza.dev}}\\
\texttt{\href{https://github.com/mehdirazajaffri}{https://github.com/mehdirazajaffri}}\\
Phone: +971 50 745 9015\\

\end{document}


