\documentclass[a4paper,11pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{times}  % Times New Roman - Most ATS-friendly serif font (RECOMMENDED)
% Alternative options (also ATS-friendly):
% \usepackage{helvet}  % Helvetica/Arial (sans-serif) - Modern and clean
% \renewcommand{\familydefault}{\sfdefault}
\usepackage{fontawesome5}
\usepackage{tikz}
\usepackage{array}

% Minimal color scheme - mostly black text for ATS compatibility
\definecolor{darkgray}{RGB}{64, 64, 64}

% Simple section formatting - ATS-friendly with underline
\titleformat{\section}
{\large\bfseries\uppercase}
{}
{0em}
{\titlerule[0.5pt]\vspace{0.4em}}

\titlespacing*{\section}{0pt}{0.8em}{0.2em}

% Custom subsection format
\titleformat{\subsection}
{\normalsize\bfseries}
{}
{0em}
{}

\titlespacing*{\subsection}{0pt}{0.5em}{0.3em}

% Optimize spacing for lists
\setlist[itemize]{noitemsep, topsep=3pt, leftmargin=18pt, itemsep=2pt, parsep=0pt}
\setlist[enumerate]{noitemsep, topsep=3pt, leftmargin=18pt, itemsep=2pt, parsep=0pt}

% Paragraph spacing
\setlength{\parindent}{0pt}
\setlength{\parskip}{5pt}

\begin{document}

% Header with name and contact info - ATS-friendly plain text
\begin{center}
    {\Huge \textbf{MEHDI RAZA}}\\[0.3em]
    \vspace{0.2em}
    \color{darkgray}
    \faMapMarker\ Dubai, United Arab Emirates \quad
    \faPhone\ +971 50 745 9015 \quad
    \faEnvelope\ \href{mailto:mehdirazajaffri@gmail.com}{mehdirazajaffri@gmail.com}\\[0.2em]
    \faAward\ UAE Golden Visa \quad
    \faLinkedin\ \href{https://linkedin.com/in/mehdi-raza-jaffri}{linkedin.com/in/mehdi-raza-jaffri} \quad
    \faGlobe\ \href{https://mehdirazajaffri.github.io}{mehdirazajaffri.github.io}
\end{center}



\section*{Professional Summary}

Software engineer with 8+ years of experience in designing and delivering scalable, microservices-based, and AI-driven applications across fintech, e-commerce, and lifestyle domains.

\begin{itemize}[leftmargin=*]
    \item Specialized in Python, FastAPI, Django, and Java, with strong expertise in AWS serverless architectures and cloud-native microservices built for performance, reliability, and maintainability.
    \item Skilled in leveraging AI/ML platforms such as LangChain, RAG pipelines, and SageMaker to automate workflows, enhance decision-making, and improve business efficiency.
    \item Delivered measurable impact, including a 15\% boost in transaction success rates through ML optimization and a 70\% reduction in deployment time via DevOps automation.
    \item Motivated by innovation, ownership, and collaboration, and passionate about contributing to teams that value technical excellence, experimentation, and continuous improvement.
\end{itemize}


\section*{Technical Skills}
\begin{itemize}[leftmargin=*]
    \item \textbf{Backend \& APIs:} Python, FastAPI, Django, Django REST Framework, Flask, Java, Spring Boot, Node.js, Express.js, Go
    \item \textbf{Cloud \& Serverless:} AWS Lambda, Step Functions, API Gateway, EC2, ECS, CloudFront, Cognito, CloudFormation, Terraform, AWS CDK, Serverless Framework
    \item \textbf{Data, AI/ML \& Analytics:} LangChain, LangGraph, AWS SageMaker, Glue, Pandas, PyTorch, scikit-learn, OpenCV, RAG pipelines
    \item \textbf{Frontend \& Mobile:} React, Next.js, TypeScript, React Native, Flutter
    \item \textbf{DevOps \& Automation:} Docker, Jenkins, GitHub Actions, Bitbucket Pipelines, Ansible, SAM CLI, Vercel
    \item \textbf{Messaging \& Integrations:} NATS, SNS, SQS, Stripe, Telr, PayPal, Checkout.com, Firebase, Twilio, SendGrid, Prismic
    \item \textbf{Observability \& Reliability:} Datadog, CloudWatch, Grafana, Kibana, New Relic, Sentry
    \item \textbf{Databases \& Storage:} PostgreSQL, MySQL, DynamoDB, MongoDB
    \item \textbf{Architecture:} Microservices, Serverless Design, Event-driven Systems, REST, GraphQL
\end{itemize}

\section*{Professional Experience}

\subsection*{Senior Software Engineer \hfill Jan 2024 -- Present}
\textit{Aether $|$ Dubai, UAE $|$ Remote}
\vspace{0.2em}
\begin{itemize}
    \item Architected an ML-based rebill optimization system using AWS Glue and SageMaker, increasing successful transaction rates by 15\% through intelligent retry timing.
    \item Developed an AI-powered chatbot with RAG-based query generation, reducing manual data lookup time by 80\% and supporting over 100 internal users with real-time business insights. Deployed fine-tuned LLMs via SageMaker endpoints for production inference.
    \item Designed and developed microservices-based backend systems for e-commerce, memberships, and chat platforms using FastAPI, Java Spring Boot, and MongoDB, leveraging AWS Lambda, ECS, and API Gateway.
    \item Automated deployment pipelines using Ansible, Docker, and Jenkins, reducing setup and provisioning time by 70\%.
    \item Led the implementation of a NATS messaging architecture with clustered configuration and custom authentication, improving system reliability by 40\% and reducing latency by 50\%.
    \item Collaborated with cross-functional teams to deliver high-quality, production-ready solutions.
\end{itemize}

\subsection*{Lead Full-Stack Developer \hfill May 2022 -- Dec 2023}
\textit{OJ Lifestyle $|$ Dubai, UAE}
\vspace{0.2em}
\begin{itemize}
    \item Led end-to-end agile development lifecycle, from requirements gathering to production deployment, improving team delivery velocity by 30\%.
    \item Designed and implemented the core architecture for a loyalty platform, taking it from prototype to production with FastAPI, Django, and Java-based microservices, supporting over 5,000 active user subscriptions annually.
    \item Developed and launched a vendor-facing portal, empowering 50+ vendors to manage coupons and offers independently, increasing vendor engagement by 40\%.
    \item Integrated Stripe’s subscription management system to support recurring payments, achieving a 99.99\% payment success rate and reducing churn-related issues by 25\%.
    \item Streamlined CI/CD pipelines using GitHub Actions and Vercel, reducing deployment time by 60\% and increasing release frequency.
    \item Implemented a dynamic and responsive front-end using React.js and Next.js, enhancing cross-device user experience and improving user satisfaction scores by 35\%.
    \item Established automated testing and monitoring processes, reducing post-release defects by 50\% and achieving 90\% code coverage through comprehensive unit testing.
\end{itemize}

\subsection*{Full Stack Developer \hfill Mar 2021 -- Apr 2022}
\textit{Berkeley Assets $|$ Dubai, UAE}
\vspace{0.2em}
\begin{itemize}
    \item Collaborated with UK team to build and maintain internal CRMs, boosting productivity by 25\% through automation.
    \item Led end-to-end project delivery, from concept to deployment, ensuring on-time, high-quality releases.
    \item Developed a custom Django Admin back office with DRF APIs and integrated payment gateways (Stripe, Telr), achieving 99.9\% transaction reliability.
    \item Built cross-platform apps using React Native, increasing delivery speed by 40\%.
    \item Designed a scalable, serverless backend using AWS Lambda, Django, and AWS Fargate, cutting infrastructure costs by 30\%.
    \item Delivered stable, fault-tolerant systems with zero major incidents post-launch.
    \item Conducted usability testing and incorporated user feedback, leading to a 45\% improvement in user satisfaction and task completion rates.
\end{itemize}

\subsection*{Software Developer \hfill Jan 2020 -- Mar 2021}
\textit{sellanycar.com $|$ Dubai, UAE}
\vspace{0.2em}
\begin{itemize}
    \item Developed an AWS-based serverless image processing system in Python using OpenCV, efficiently handling millions of uploaded images and reducing processing time by 40\%.
    \item Integrated microservices with GraphQL, improving system performance by 30\%.
    \item Integrated WebSocket support in the mobile app using Ionic and Apollo Server to enable real-time updates for customers.
    \item Optimized orchestration by coordinating AWS Lambdas with AWS Step Functions, reducing execution time by 50\%.
    \item Established CI/CD pipelines using Jenkins and Bitbucket Pipelines, enabling automated deployments and reducing manual deployment errors by 90\%.
    \item Achieved 99\% code coverage through comprehensive unit testing and post-production validation, ensuring high code quality and system reliability.
    \item Optimized database queries and indexing strategies, resulting in a 60\% reduction in query response time and improved application performance.
    \item Leveraged a diverse cloud-native stack, including Serverless Framework, GraphQL, Node.js, and Python.
\end{itemize}

\subsection*{Senior Software Engineer \hfill Dec 2018 -- Dec 2019}
\textit{VentureDive $|$ Karachi, Pakistan}
\vspace{0.2em}
\begin{itemize}
    \item Full Stack Developer at zGlue $|$ Contracted through VentureDive $|$ designed and developed software applications for the zGlue ChipBuilder CAD platform using Python, Node.js, and React.
    \item Architected features for zGlue ChipBuilder, enabling customers to design, visualize, and manufacture custom integrated circuits by combining IoT components.
    \item Delivered production-grade services with Django Admin and DRF APIs, integrating Stripe, Telr, and Checkout.com to maintain 99.9\% transaction reliability.
    \item Created cross-platform React Native applications that accelerated feature delivery by 40\% across mobile channels.
    \item Introduced serverless patterns on AWS Lambda and Fargate, lowering infrastructure costs by 30\% while maintaining zero major post-launch incidents.
    \item Collaborated with UK stakeholders to modernize internal CRMs, boosting team productivity by 75\% through automation.
\end{itemize}

\subsection*{Software Engineer \hfill Feb 2016 -- Nov 2018}
\textit{VentureDive $|$ Karachi, Pakistan}
\vspace{0.2em}
\begin{itemize}
    \item Engineered and maintained microservices-based systems for \textit{vistajet.com} as a Full Stack Developer, collaborating with remote teams in Brazil and Ukraine to build enterprise-scale applications using React, MySQL, Java Spring Boot, Episerver, and Jenkins.
    \item Led full-stack development for client-facing platforms at \textit{servicemarket.com}, delivering scalable portals using CakePHP, Django, Angular, and React/Redux.
    \item Partnered with cross-functional teams in Dubai to design data-driven solutions, integrating Tableau dashboards and Ratabase for real-time insurance pricing and analytics.
    \item Streamlined CI/CD processes using Jenkins and Git, ensuring consistent, reliable, and automated deployments across multi-tenant environments.
\end{itemize}

\vspace{0.8em}
\section*{Education}
\begin{itemize}[leftmargin=*]
    \item \textbf{Bachelor of Computer Science} \hfill 2012 -- 2015\\
    \textit{University of Karachi}
\end{itemize}

\vspace{0.8em}
\section*{Certifications and Awards}
\begin{itemize}[leftmargin=*]
    \item \textit{AWS Certified Solutions Architect - Associate} \hfill 2016 -- 2018
    \item \textit{X-Factor Award (Venturedive's Hackathon)} \hfill 2018
\end{itemize}

\end{document}